% update chapters
% update NSF grant
%________________________________________________________________________________________
% @brief    LaTeX2e Resume for C. Titus Brown
% @author   Titus Brown
% @date     January 2008
% @info     Based on Latex Resume Template by Chris Paciorek 
%           http://www.biostat.harvard.edu/~paciorek/


%________________________________________________________________________________________
\documentclass[margin,line]{resume}

\usepackage{hyperref}
\usepackage{color}
\hypersetup{urlcolor=blue}

\begin{document}
\name{\Large C. Titus Brown}
\pagenumbering{arabic}
\pagestyle{plain}


\begin{resume}


    %____________________________________________________________________________________

    {\small (As of May 2014.)}

    % Education
    \section{\mysidestyle Professional Preparation}

    {\bf Reed College}, Portland, OR; Mathematics; B.A., 1997

    \vspace{2mm}

    {\bf California Institute of Technology}, Davidson Lab (graduate student);
\\
Developmental Biology; PhD., 2007

    \vspace{2mm}

    {\bf California Institute of Technology}, Bronner-Fraser Lab (postdoc);\\
 Developmental Biology and Bioinformatics; 2007-2008

    \vspace{2mm}

    \section{\mysidestyle Appointments}

    {\bf Assistant Professor}, 
Microbiology \& Molecular Genetics / Computer Science and Engineering\\
Michigan State University, 2008-present.

    %____________________________________________________________________________________
    % Honours and Awards
    \section{\mysidestyle Honours and\\Awards} 

Burroughs-Wellcome Fund Computational Biology Fellowship (1999-2004).\\
Withrow Award for Teaching Excellence in Computer Science (2008-2009). \\
Woods Hole Marine Biological Laboratory Summer Fellow (2013).\\
Michigan State University / College of Natural Science Teacher-Scholar Award (2013).


    \section{\mysidestyle Synergistic Activities}

\begin{list1}
\item[] 1. Personal/professional blog at: \href{http://ivory.idyll.org/blog/}{ivory.idyll.org/blog/}.  A few selected posts: \href{http://ivory.idyll.org/blog/replication-i.html}{``Our approach to replication in computational science''}, \href{http://ivory.idyll.org/blog/thoughts-on-assemblathon-2.html}{``Thoughts on Assemblathon 2''}, \href{http://ivory.idyll.org/blog/the-future-of-khmer-2013-version.html}{``The future of khmer (2013)''}.  150,000 visitors, 80,000 unique (Feb 2013-Feb 2014).
\item[] 2. Course director, 2010-present, Next-Generation Sequence Analysis for Biologists, KBS, MSU.  Open materials at \href{http://ged.msu.edu/angus/}{ged.msu.edu/angus/}. Over 500 applicants in four years.
\item[] 3. iPlant Collaborative Scientific Advisory Board member.  iPlant Collaborative is a large NSF BIO Cyberinfrastructure project focused on genomics and phenomics research.
\item[] 4. Software Carpentry Advisory Board member.
\item[] 5. Member of the Python Software Foundation.

\end{list1}

    \section{\mysidestyle Papers and Projects}

{\em Full publication list at: http://scholar.google.com/citations?user=O4rYanMAAAAJ}

{\em khmer: k-mer counting and filtering FTW.} Software project, at http://github.com/ged-lab/khmer/. Michael R. Crusoe, Greg Edvenson, Jordan Fish, Adina Howe, Eric McDonald, Joshua Nahum, Kaben Nanlohy, Jason Pell, Jared Simpson, C. S. Welcher, Qingpeng Zhang, and C. Titus Brown.  BSD license. Estimated $\approx$ 200 users; 32 GitHub stars (93-99\%ile); 56 GitHub forks (97-100\%ile)

{\em Tackling soil diversity with the assembly of large, complex metagenomes.} Howe AC, Jansson J, Malfatti SA, Tringe SG, Tiedje JM, {\bf Brown CT}. Proc Natl Acad Sci USA, 2014, \\
doi: 10.1073/pnas.1402564111. (2 cit.)

{\em A Reference-Free Algorithm for Computational Normalization of Shotgun Sequencing Data.} {\bf Brown CT}, Howe AC, Zhang Q, Pyrkosz AB, Brom TH. preprint arXiv:1203.4802. (15 cit.)

{\em Scaling metagenome sequence assembly with probabilistic de Bruijn
graphs.} Pell J, Hintze A, Canino-Koning R, Howe A, Tiedje JM, {\bf Brown
  CT}. Proc Natl Acad Sci USA, published online before print July 30,
  2012, doi: 10.1073/pnas.1121464109. (41 cit.)

{\em Exploring the future of bioinformatics data sharing and mining
  with Pygr and Worldbase} Lee C, Alekseyenko A, {\bf Brown CT}.  in {\em
  Proceedings of the 8th Python in Science conference (SciPy 2009)}, G
Varoquaux, S van der Walt, J Millman (Eds.), pp. 62-67.  (4 cit.)

\newpage

    \section{\mysidestyle Other Works}

{\em Best practices for scientific computing.} Wilson GV et al. PLoS biology 12 (1), e1001745.  (25 citations)

{\em Reproducible Bioinformatics Research for Biologists}.  Preeyanon
L, Pyrkosz AB, and Brown CT. Chapter in Implementing Reproducible
Computational Research, V. Stodden and R. Peng, ed.  Forthcoming in
Dec 2013; \href{https://osf.io/api/v1/project/pk46g/files/download/Brown_chapter.pdf/version/1/}{(link)}

{\em A genomic
regulatory network for development.}\\
Davidson EH, Rast JP, Oliveri P, Ransick A, Calestani C, Yuh CH,
Minokawa T, Amore G, Hinman V, Arenas-Mena C, Otim O, {\bf Brown CT}, Livi
CB, Lee PY, Revilla R, Rust AG, Pan Z, Schilstra MJ, Clarke PJ, Arnone
MI, Rowen L, Cameron RA, McClay DR, Hood L, Bolouri H.
\\Science. 2002 Mar
1;295(5560):1669-78.  PMID: 11872831. (1083 cit.)

{\em Earthshine observations of the earth's reflectance}
P. R. Goode, J. Qiu, V. Yurchyshyn, J. Hickey, M.-C. Chu, E. Kolbe, C. T. Brown, and S. E. Koonin
Geophys. Res. Lett. 28, 1671 (2001). (95 cit.)

{\em Evolutionary Learning in the 2D Artificial Life System ``Avida''}\\
Adami C, Brown CT. Proc. of ``Artificial Life IV'', MIT Press, p. 377-381
(1994).  (198 cit.)

\section{\mysidestyle Collaborators}

J. Barrick (UT Austin), J. Bell (MSU), H. Cheng (MSU), S. Goffredi (Caltech), C. Lee (UCLA), L. Mansfield (MSU), P.W. Sternberg (Caltech), B.J. Swalla (UW), J.M. Tiedje (MSU), S.G. Tringe (JGI), J.Jansson (JGI)., W. Warren (WUSTL), E. White (USU), G.V. Wilson (Mozilla).

Graduate advisor:  Eric H. Davidson (Caltech); Postdoctoral: Marianne Bronner (Caltech)

    %____________________________________________________________________________________

\vspace{1cm}

\end{resume}

\end{document}

%________________________________________________________________________________________
% EOF


R
