% update chapters
% update NSF grant
%________________________________________________________________________________________
% @brief    LaTeX2e Resume for C. Titus Brown
% @author   Titus Brown
% @date     January 2008
% @info     Based on Latex Resume Template by Chris Paciorek 
%           http://www.biostat.harvard.edu/~paciorek/


%________________________________________________________________________________________
\documentclass[margin,line]{resume}

\usepackage{hyperref}
\usepackage{color}
\hypersetup{urlcolor=blue}

\begin{document}
\name{\Large C. Titus Brown}
\pagenumbering{arabic}
\pagestyle{plain}


\begin{resume}


    %____________________________________________________________________________________

%    {\small (As of Feb 2015.)}

    % Education
    \section{\mysidestyle Education}

    {\bf Reed College}, Portland, OR; Mathematics; B.A., 1997

    \vspace{2mm}

    {\bf California Institute of Technology}, Davidson Lab (graduate student);
\\
Developmental Biology; PhD., 2007

    \vspace{2mm}

    {\bf California Institute of Technology}, Bronner-Fraser Lab (postdoc);\\
 Developmental Biology and Bioinformatics; 2007-2008

    \vspace{2mm}

    \section{\mysidestyle Appointments}

    {\bf Assistant Professor}, 
Microbiology \& Molecular Genetics / Computer Science and Engineering\\
Michigan State University, 2008-2014.

    {\bf Associate Professor}, 
Population Health and Reproduction, School of Veterinary Medicine \\
University of California Davis, Jan 2015-July 2021.

    {\bf Professor}, 
Population Health and Reproduction, School of Veterinary Medicine \\
University of California Davis, July 2021-present.

    {\bf Faculty Directory of Community Initiatives}, UC Davis DataLab. \\
    University of California Davis, November 2020-present.

    %____________________________________________________________________________________
    % Honours and Awards
    \section{\mysidestyle Honours and\\Awards} 

Burroughs-Wellcome Fund Computational Biology Fellowship (1999-2004).\\
Withrow Award for Teaching Excellence in Computer Science (2008-2009). \\
Woods Hole Marine Biological Laboratory Summer Fellow (2013).\\
Michigan State University / College of Natural Science Teacher-Scholar Award (2013).\\
{\bf Moore Foundation Data Driven Discovery Investigator (2014-2019).}


    %____________________________________________________________________________________
    % Publications

    \section{\mysidestyle Publications}

    Full publication list: {\em http://scholar.google.com/citations?user=O4rYanMAAAAJ}\\
    Blog: {\em http://ivory.idyll.org/blog/}\\
    Twitter: {\em http://twitter.com/ctitusbrown}\\
    ImpactStory: {\em https://profiles.impactstory.org/u/0000-0001-6001-2677}

    \section{\mysidestyle Software Development and Maintenance}

    Active open source developer at http://github.com/ctb/ and http://github.com/dib-lab/.

    Active projects include:
    \begin{list1}
    \item[] - sourmash, large-scale sequence search by content;
    \item[] - spacegraphcats, metagenome assembly graph query;
    \item[] - genome-grist, workflow for shotgun metagenome decomposition;
    \item[] - charcoal, large-scale genome decontamination analysis;
    \end{list1}

    \section{\mysidestyle Professional\\Activities}

    \begin{list1}
\item[] - Co-lead, NIH Data Commons Pilot Phase Consortium, 2017-2019.
\item[] - Lead, Engagement and Training, NIH Common Fund Data Ecosystem, 2019-present.
\item[] - Member, Advisory Board member for the West Big Data Hub.
\item[] - Member, Scientific Advisory Board for CZI HCA.
\item[] - Member, Executive Advisory Board for the Maine NIH INBRE grant.
\item[] - Software Carpentry Scientific Advisory Board member (2008-2012).
\item[] - Accredited Carpentries Instructor.
\item[] - Course director, 2010-2019, Next-Generation Sequence Analysis for Biologists.
\item[] - Course faculty, 2006-2008, Embryology Course, Woods Hole Marine Biological Laboratory.
\item[] - Course faculty, 2015-2019, Strategies and Techniques for Analyzing Microbial - Population Structure (STAMPS), Woods Hole Marine Biological Laboratory.
\item[] - Reviewer for NSF, NIH, Moore Foundation, and Sloan Foundation.
\item[] - Several now-unmaintained open source bioinformatics tools, including
  Cartwheel server for comparative sequence analysis, khmer k-mer software.
\item[] - Moderator, python-ideas mailing list, 2019-present.
\end{list1}

\vspace{2cm}
    

\end{resume}

\end{document}

%________________________________________________________________________________________
% EOF


