% update chapters
% update NSF grant
%________________________________________________________________________________________
% @brief    LaTeX2e Resume for C. Titus Brown
% @author   Titus Brown
% @date     January 2008
% @info     Based on Latex Resume Template by Chris Paciorek 
%           http://www.biostat.harvard.edu/~paciorek/


%________________________________________________________________________________________
\documentclass[margin,line]{resume}

\usepackage{hyperref}
\usepackage{color}
\hypersetup{urlcolor=blue}

\begin{document}
\name{\Large C. Titus Brown}
\pagenumbering{arabic}
\pagestyle{plain}


\begin{resume}


    %____________________________________________________________________________________

    {\small (As of July 2017.)}

    % Education
    \section{\mysidestyle Education}

    {\bf Reed College}, Portland, OR; Mathematics; B.A., 1997

    \vspace{2mm}

    {\bf California Institute of Technology}, Davidson Lab (graduate student);
\\
Developmental Biology; PhD., 2007

    \vspace{2mm}

    {\bf California Institute of Technology}, Bronner-Fraser Lab (postdoc);\\
 Developmental Biology and Bioinformatics; 2007-2008

    \vspace{2mm}

    \section{\mysidestyle Appointments}

    {\bf Assistant Professor}, 
Microbiology \& Molecular Genetics / Computer Science and Engineering\\
Michigan State University, 2008-2014.

    {\bf Associate Professor}, 
Population Health and Reproduction, School of Veterinary Medicine \\
University of California Davis, 2015-present.

    %____________________________________________________________________________________
    % Honours and Awards
    \section{\mysidestyle Honours and\\Awards} 

Burroughs-Wellcome Fund Computational Biology Fellowship (1999-2004).\\
Withrow Award for Teaching Excellence in Computer Science at MSU (2008-2009). \\
Woods Hole Marine Biological Laboratory Summer Fellow (2013).\\
Michigan State University / College of Natural Science Teacher-Scholar Award (2013).\\
{\bf Moore Foundation Data Driven Discovery Investigator (2014-2019).}


    \section{\mysidestyle Peer Reviewed Publications}

{\em Full publication list at: http://scholar.google.com/citations?user=O4rYanMAAAAJ\\
  March 2016: 5090 citations total; h-index of 29, i10-index of 38.}

{\em Centromere location in Arabidopsis is unaltered by extreme divergence in CENH3 protein sequence.} S Maheshwari, T Ishii, CT Brown, A Houben, L Comai. Genome Research 27 (3), 471-478. 2017.

{\em Tissue resolved, gene structure refined equine transcriptome.} A Mansour, EY Scott, CJ Finno, RR Bellone, MJ Mienaltowski, MC Penedo, PJ Ross, SJ Valberg, JD Murray, CT Brown. BMC Genomics 18 (1) p103. 2017.

{\em A new chicken genome assembly provides insight into avian genome structure}. WC Warren et al. G3 7 (1) 109-117. 2017.

{\em Transcriptome of the Caribbean stony coral Porites astreoides from three developmental stages.} Mansour TC, Rosenthal JJC, Brown CT, Roberson LM.
GigaScience 5 (1), 33, August 2016.

{\em How open science helps researchers succeed.}
McKiernan EC et al., eLife 5, e16800, July 2016.

{\em Haplotype-phased synthetic long reads from short-read sequencing.}
JA Stapleton, et al.,
PLOS One 11 (1), e0147229, 2016.

{\em Microbial community analysis with ribosomal gene fragments from shotgun metagenomes.} Guo J, Cole JC, Zhang Q, Brown CT, Tiedje JM. Applied and environmental microbiology. Jan 2016.

{\em Haplotype-phased synthetic long reads from short-read sequencing.} Stapleton JA, Kim J, Hamilton JP, Wu M, Irber LC, Maddamsetti R, Briney B, Newton L, Burton DR, Brown CT, Chan C, Buell CR, Whitehead TA. PLOS One. Jan 2016.

{\em Hsp90 and hepatobiliary transformation during sea lamprey metamorphosis.}
Chung-Davidson YW, Yeh CY, Bussy U, Li K, Davidson PJ, Nanlohy KG, Brown CT, Whyard S, Li W. BMC Developmental Biology. Dec 2015.

\newpage

{\em A new method for DNA sequencing error verification and correction via an on-disk index tree}. Gu Y, Liu X, Zhu Q, Dong Y, Brown CT, Pramanik S.  Proceedings of the 6th ACM Conference on Bioinformatics, Computational Biology and Health Informatics. Sep 2015.

{\em Differentially-Expressed Pseudogenes in HIV-1 Infection.} Gupta A, Brown CT, Zheng YH, Adami C. Viruses. Sep 2015.

{\em The khmer software package: enabling efficient nucleotide sequence analysis.} Crusoe MR et al., Brown CT. F1000Research. Sep 2015.

{\em Xander: employing a novel method for efficient gene-targeted metagenomic assembly.} Wang Q, Fish JA, Gilman M, Sun Y, Brown CT, Tiedje JM, Cole JR. Microbiome. August 2015.

(11 publications omitted for space reasons)

\section{\mysidestyle Invited Articles and Reviews}

{\em Strain recovery from metagenomes. Brown CT.} Nature Biotechnology
33 (10), 1041-1043, Oct 2015.

{\em Metagenomics: the paths forward}.  Brown CT and Tiedje JM.
Handbook of Molecular Microbiology II: Metagenomics in Different
Habitats.  Wiley-Blackwell 10 Nov 2011.

{\em Computational approaches to finding and analyzing cis-regulatory elements.} 
Brown CT. Methods Cell Biol. 2008;87:337-65. Review.
PMID: 18485306  (7 cit.)

{\em Reproducible Bioinformatics Research for Biologists}.  Preeyanon
L, Pyrkosz AB, and Brown CT. Chapter in Implementing Reproducible
Computational Research, V. Stodden and R. Peng, ed.  Forthcoming in
Dec 2013.

\section{\mysidestyle Reports and Editorials}

{\em Cephalopod genomics: A plan of strategies and organization.} Albertin et al., Standards in Genomic Sciences 7 (1), 175. (2 cit.)

{\em Changing computational research. The challenges ahead.}
Neylon, C., Aerts, J., Brown, C.T., Lemire, D., Millman, J., Murray-Rust, P., Perez, F., Saunders, N., Smith, A., Varoquaux, G.
Source Code for Biology and Medicine 7 (1), 2 (2012). (3 cit.)

{\em Meeting report: the terabase metagenomics workshop and the vision of an Earth microbiome project.}
Gilbert, J.A., Meyer, F., Antonopoulos, D., Balaji, P., Brown, C.T., Brown, C.T., Desai, N., Eisen, J.A., Evers, D., Field, D. Standards in genomic sciences, 3(3) 243 (2010). (41 cit.)

\section{\mysidestyle Online commentaries, blogs, and social media}

Personal/professional blog at: \href{http://ivory.idyll.org/blog/}{ivory.idyll.org/blog/}.  A few selected posts (click on links): \href{http://ivory.idyll.org/blog/replication-i.html}{``Our approach to replication in computational science''}, \href{http://ivory.idyll.org/blog/thoughts-on-assemblathon-2.html}{``Thoughts on Assemblathon 2''}, \href{http://ivory.idyll.org/blog/the-future-of-khmer-2013-version.html}{``The future of khmer (2013)''}.

Twitter: \href{http://twitter.com/ctitusbrown}{@ctitusbrown}

\href{http://blogs.biomedcentral.com/bmcblog/2013/02/28/version-control-for-scientific-research/}{BioMedCentral invited blog post: ``Version control for scientific research''}

\section{\mysidestyle Selected Invitations and Meetings}

\begin{list1}

\item[] April 2013 - NIH NHGRI Education and Training committee.
\item[] March 2013 - Invited speaker at National Center for Atmospheric Research Software Engineering Assembly.
\item[] March 2013 - NSF/Moore Foundation meeting on Cyberinfrastructure for Marine 'Omics.
\item[] September 2012 - Invited speaker at Extremely Large Databases 2012 (XLDB 2012).
\item[] June 2012 - NSF BIO Centers meeting on Cyberinfrastructure Needs in BIO.

\end{list1}

\end{resume}

\end{document}

%________________________________________________________________________________________
% EOF


